Simulating Data from the GSS

### 2023-03-12 outputs/paper/paper.qmd
Update attributions

---
title: "Does Happiness Lead to Altruism: A review of US Generial Social Survey data"
format: pdf
author: "Sebastian Rodriguez, Iz Leitch, Randall Ni"
abstract: "Something about happiness and altruism" 
date: today
date-format: long
editor: visual
toc: TRUE
number-sections: TRUE
bibliography: references.bib
thanks: "Code and data supporting this analysis is available at: https://github.com/seb646/happiness-and-altruism"
---

```{r}
#| messages: false
#| echo: false
#| warning: false
#| output: false
#### Preamble ####
# Title: The Response Time of Toronto's Paramedic Service: How effective is the city's emergency medical care?
# Author: Sebastian Rodriguez
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/toronto-paramedic-responses

@@

The General Social Survey (GSS) is a project of the independent research organization NORC at the University of Chicago, with principal funding from the National Science Foundation.

>>>>

---
title: "Does Happiness Lead to Altruism: A review of US General Social Survey data"
format: pdf
author: "Sebastian Rodriguez, Iz Leitch, Randall Ni"
abstract: "Something about happiness and altruism" 
date: today
date-format: long
editor: visual
toc: TRUE
number-sections: TRUE
bibliography: references.bib
thanks: "Code and data supporting this analysis is available at: https://github.com/seb646/happiness-and-altruism"
---

```{r}
#| messages: false
#| echo: false
#| warning: false
#| output: false
#### Preamble ####
# Title: Does Happiness Lead to Altruism: A review of US General Social Survey data
# Author: Sebastian Rodriguez, Iz Leitch, Randall Ni
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/happiness-and-altruism

@@

### 2023-03-12 scripts/03-data_testing.qmd
Update attributions

---
title: "Testing Data from the Toronto Paramedic Service"
format: html
author: "Sebastian Rodriguez"
---
```{r}
#### Preamble ####
# Purpose: Testing Data from the Toronto Paramedic Service
# Prerequisites: Need to have downloaded the data using [inputs/data/data_import.qmd]
# Author: Sebastian Rodriguez
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/toronto-paramedic-responses

>>>>

---
title: "Testing Data from the GSS"
format: html
author: "Sebastian Rodriguez, Iz Leitch, Randall Niz"
---
```{r}
#### Preamble ####
# Purpose: Testing Data from the GSS
# Prerequisites: Need to have downloaded the data using [inputs/data/data_import.qmd]
# Author: Sebastian Rodriguez, Iz Leitch, Randall Ni
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/happiness-and-altruism

### 2023-03-12 scripts/04-data_simulation.qmd
Update attributions

---
title: "Simulating Data from the Toronto Paramedic Service"
format: html
author: "Sebastian Rodriguez"
---
```{r}
#### Preamble ####
# Purpose: Read in data from the Toronto Paramedic Service
# Prerequisites: Need to know where to get Toronto Paramedic Services data
# Author: Sebastian Rodriguez
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/toronto-paramedic-responses

>>>>

---
title: "Simulating Data from the GSS"
format: html
author: "Sebastian Rodriguez, Iz Leitch, Randall Ni"
---
```{r}
#### Preamble ####
# Purpose: Read in data from the GSS
# Prerequisites: Need to know where to get GSS data
# Author: Sebastian Rodriguez, Iz Leitch, Randall Ni
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/happiness-and-altruism
